A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-19 0_main.tex
all authors
first complete version of related work - Jun
describe dataset
gMAT print photos
undor draft option
zjenja: minor changes and corrections

\documentclass[5p,twocolumn,10pt,times]{elsarticle}
\usepackage{amsmath}
\usepackage{hyperref}
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

@@

	\newlength{\figwidth}
	\newlength{\figheight}

@@

\author[um,tud]{Tim Kuipers}
%\author[tud]{Jun Wu}
%\author[cuhk]{Charlie Wang{\corref{cor1}}}
%\ead{cwang@mae.cuhk.edu.hk}
%\cortext[cor1]{Corresponding author}
\address[um]{Ultimaker, Utrecht, The Netherlands}
\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
%\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
FDM works by depositing material along paths which lie in horizontal layers.
The outlines of each layer are filled (partly) using contour-following toolpaths approximately the size of the printing nozzle.
Filling the outlines with extruded material densely and accurately is important for fabricating parts accurately and stiffly.
An accurate dense filling is aspecially important to thin parts such as casings for electronics, blowmolding prototypes, (architectural) models and microstructures.

@@

\end{document}

>>>>

\documentclass[5p,twocolumn,10pt,times]{elsarticle}
\usepackage{amsmath}
\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

@@

	\newlength{\figwidth}
	\newlength{\figheight}
	\newlength{\figheightTwo}

@@

\author[um,tud]{Tim Kuipers}
\author[tud]{Eugeni L. Doubrovski}
\author[tud]{Jun Wu}
\author[cuhk]{Charlie Wang{\corref{cor1}}}
\ead{cwang@mae.cuhk.edu.hk}
\cortext[cor1]{Corresponding author}
\address[um]{Ultimaker, Utrecht, The Netherlands}
\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
FDM builds up objects by depositing material along paths which lie in horizontal layers.
The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
Filling the outlines with extruded material densely is important for fabricating parts with high stiffness and dimensional accuracy.
An accurate dense filling is especially important for thin parts such as casings for electronics, blowmolding prototypes, (architectural) models, and microstructures.

@@

\begin{appendices}

\input{20_dataset}

\end{appendices}
\end{document}

### 2019-08-19 1_intro.tex
zjenja: minor changes and corrections

Fused Deposition Modeling (FDM) is one of the most common 3D printing techniques.
It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
FDM printers are used for example in showcasing scale models of buildings, casings for electronics, prototypes blowmold parts, jigs and fixtures - to name just some.
Recent research developments have investigated manufacturing complex volumetric structures such as microstructures, topology optimized structures and infill structures.
Quite some of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.

FDM printers expel molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
Because the positioning system generally has an order of magnitude better resolution than the width of the nozzle,
the toolpaths for filling the arbitrary polygonal shape of a layer with extrusion beads are following the contour of that layer.

The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the size of the hole in the nozzle from the outline shape.
However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfll} areas.
See \cref{intro_wedge}(top).
Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
Underfills on the other hand can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are large compared to the whole part.
In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
Some such toolpath generation techniques have already been developed.

@@

There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads. \cite{N.Turner2014,ahn2002anisotropic}
In order to accurately fabricate a part restricted to prescribed mechanical properties we need to generate toolpaths using the corresponding process parameters as close as possible.
We therefore develop a parametric system which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width then existing techniques.
See \cref{intro_wedge}(bottom).

>>>>

Fused Deposition Modeling (FDM) is one of the most common 3D printing techniques.
It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes blowmold parts, jigs and fixtures.
Recent research developments have investigated manufacturing complex volumetric structures such as microstructures, topology optimized structures and infill structures.
Many of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.

FDM printers deposit molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
Because the positioning system has an order of magnitude better resolution than the width of the nozzle,
the toolpaths for filling the arbitrary polygonal shape of a layer with extrusion beads are following the contour of that layer.

The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the radius of the the nozzle from the outline shape.
However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfll} areas.
See \cref{intro_wedge}(top).
Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
Underfills on the other hand, can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are large compared to the whole part.
In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
Some such toolpath generation techniques have already been developed.

@@

There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads. \cite{N.Turner2014,ahn2002anisotropic}
In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
We therefore develop a parametric system which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
See \cref{intro_wedge}(bottom).

### 2019-08-19 2_related_work.tex
first complete version of related work - Jun
zjenja: minor changes and corrections

% This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
Given a planar contour, representing the intersection of a plane and a 3D solid object, the task is to generate a path in the domain bounded by the contour.
The nozzle is then instructed to move along the path while extruding material.
The deposited material covers the path with a certain width.
Toolpath generation is an integral part of process planning for 3D printing.
For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}.~\cite{Livesu2017CGF} .
For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
In this paper, we focus on generating toolpath that seamlessly covers the entire 2D contour.
This is sometimes called dense infill~\cite{Livesu2017CGF}.

% criteria for toolpath generation
Toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object.
There are a few desirable properties for the toolpath.
First, the path shall be as continuous as possible.
A discontinuous path requires to stop and restart material extrusion.
For certain material such as TPU, this could lead to material defects~\cite{KUIPERS2019CAD}.
Furthermore, a smooth path is often preferred.
A path with a lot of sharp turns requires to slow down the movement of the nozzle, and this consequently prolongs the printing process.
Second, the path, extended with a certain width, ideally shall cover the bounded region no voids or gaps --  underfilling, and no overlap -- overfilling. 
An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
Our method is primarily concerned with minimizing under- and overfill within slices, i.e. horizontal cross-sections.

% basic toolpath strategies and their variations
Direction parallel and contour parallel are two basic toolpath strategies.
Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
Contour parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
To reduce the number of sharp turns thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}. 
Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
This is due to the fact that the offset contour meets around the medial axis and the remaining space might not match exactly the (constant) deposition width.
To avoid problems with such gaps, hybrid approaches that combine direction and contour parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Our idea to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better coverage of the domain.
Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
However, we note that the range of possible widths is not unlimited.
For instance, printing a width that is tripple the nozzle diameter is challenging.
Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simply geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
This extension, however, inherits a problem in the original method.
From any point in the geometry skeleton to the boundary, the number of contours is constant.
Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more.
In this paper we propose an adaptive beading strategy to address this problem.

>>>>

% This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
Given a planar contour, representing the intersection of a plane and a 3D solid object, the task is to generate a path in the domain bounded by the contour.
The nozzle is then instructed to move along the path while extruding material.
The deposited material covers the path with a certain width.
Toolpath generation is an integral part of process planning for 3D printing.
For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}.~\cite{Livesu2017CGF} .
For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
In this paper, we focus on generating toolpath that seamlessly fills the entire 2D contour.
This is sometimes called dense infill~\cite{Livesu2017CGF}.

% criteria for toolpath generation
Toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object.
There are a few desirable properties for the toolpath.
First, the path shall be as continuous as possible.
A discontinuous path requires to stop and restart material extrusion.
For certain material such as TPU, this could lead to material defects~\cite{KUIPERS2019CAD}.
Furthermore, a smooth path is often preferred.
Sharp turns require to slow down the movement of the nozzle, and this consequently prolongs the printing process.
Second, the path, extended with a certain width, ideally shall cover the bounded region without voids or gaps --  underfilling, and no overlap -- overfilling. 
An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
Our method is primarily concerned with minimizing under- and overfill within slices, i.e. horizontal cross-sections.

% basic toolpath strategies and their variations
Direction parallel and contour parallel are two basic toolpath strategies.
Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
Contour parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}. 
Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
To avoid problems with such gaps, hybrid approaches that combine direction and contour parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary, there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Our approach to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
However, we note that the range of possible widths is not unlimited.
For instance, printing a width that is triple the nozzle diameter is challenging.
Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simply geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
This extension, however, inherits a problem in the original method.
From any point in the geometry skeleton to the boundary, the number of contours is constant.
Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more.
In this paper we propose an adaptive beading strategy to address this problem.

### 2019-08-19 4_method.tex
zjenja: minor changes and corrections

\subsubsection{Beading propagation}\label{section_beading_conflicts}
Because the beading information will be propagated outward from the central marked regions, beading conflicts can arise where a marked bone has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
See \cref{beading_conflict_problem}.
In such a case we will interpolate between the lower beading and the beading propagated from above,
starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
At the nodes in between we will apply the interpolation between the two beadings and propagate the interpolated beading outward from those nodes.
This interpolation is performed during the beading propagation algorithm.
\todo{Make a better figure for this.}

@@

After each marked node is assigned a beading by the beading strategy, we propagate the beadings outward to all nodes in the ST.
The beading propagation is performed in two stages: an upward stage and a downward phases.
%First we sort all upward half-edges on the radial distance of their destination node, so that we can efficiently flood fill the beading information.
In the upward phase we walk from each marked node upward along unmarked edges and map each node encountered to a pair consisting of the traversed distance and the bottom source beading.
In the downward phase we walk from each marked node downward along unmarked edges and map each node to a pair consisting of the traversed distance and the upper source beading -
however, if we encounter a node which was already mapped to an upward propagated beading we employ the interpolation scheme described above in order to define the beading, which is then further propagated downward.
This is implemented in a flood-fill fashion: see \cref{alg_beading_propagation}.

>>>>

\subsubsection{Beading propagation}\label{section_beading_conflicts}
Because the beading information will be propagated outward from the central marked regions, beading conflicts can arise where a marked bone has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
See \cref{beading_conflict_problem}.
In such a case we interpolate between the lower beading and the beading propagated from above,
starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
At the nodes in between we will apply the interpolation between the two beadings and propagate the interpolated beading outward from those nodes.
This interpolation is performed during the beading propagation algorithm.
\todo{Make a better figure for this.}

@@

After each marked node is assigned a beading by the beading strategy, we propagate the beadings outward to all nodes in the ST.
The beading propagation is performed in two stages: an upward and downward stage.
%First we sort all upward half-edges on the radial distance of their destination node, so that we can efficiently flood fill the beading information.
In the upward phase we walk from each marked node upward along unmarked edges and map each node encountered to a pair consisting of the traversed distance and the bottom source beading.
In the downward phase we walk from each marked node downward along unmarked edges and map each node to a pair consisting of the traversed distance and the upper source beading -
however, if we encounter a node which was already mapped to an upward propagated beading we employ the interpolation scheme described above in order to define the beading, which is then further propagated downward.
This is implemented in a flood-fill fashion: see \cref{alg_beading_propagation}.

### 2019-08-19 6_validation.tex
gMAT print photos
zjenja: minor changes and corrections

\section{Beading strategies}
Now that we have described a framework for deciding and applying on bead counts and their widths locally, we can introduce several beading strategies which determine the bead count and their widths in different ways.
We can emulate a variety of toolpath generation methods from related literature by meticulously defining new beading strategies.
We also introduce new beading strategies which produce toolpaths with less extremal widths then techniques from existing literature.

A beading strategy was defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.
Most of the beading strategies we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_\text{pref} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( b^{-1}(n) / w_\text{pref}  - n \right) \\
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

@@

\section{Validation}
In order to test our framework we have assembled a data set of various types of 3D model, ranging over various applications and various types of geometry.
The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the dataset and selected 300 random slices from the total set of slices for thorough analysis.
We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the constant bead count strategy with a bead count of $C=4$, the centered beading strategy, the evenly distributed and the inward distributed beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

@@

We calculated the total overfill and underfill areas of the different toolpath strategies applied on the dataset. 
The overfill and underfill area as a percentage of the total area of the slices from the dataset are illustrated in \cref{over_underfill}.  
The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to on dataset.

@@

\paragraph{Uniformity}
Depending on the printer hardware configuration, some bead widths might be difficult or impossible to manufacture.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
Also, large bead widths can cause the extruded material to upwards instead of filling the required width.
\todo{Include picture of flutter?}
Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.

@@

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive segments generated by each strategy.
The relative frequency of these angles is shown in \cref{smoothness}.
All strategies show a higher number of corners below 45 degrees, with a peak towards 0 degrees.
While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the remaining strategies.

@@

The resulting prints are viewed in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the depositioning control system some of the prints show defects.
Such defects are less prevalant for the inward distributed beading strategy than the other strategies.

@@

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
\caption{Naive}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the naive strategy, center deivation strategy and the inward distributed strategy.
The naive method produces distinct underfill areas.
The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed strategy produces the least defects.
}
\label{prints}
\end{figure}

@@

We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.

>>>>

\section{Beading strategies}
Now that we have described a framework for deciding and applying on bead counts and their widths locally, we can introduce several beading strategies which determine the bead count and their widths in different ways.
We can emulate a variety of toolpath generation methods from related literature by meticulously defining new beading strategies.
We also introduce new beading strategies which produce toolpaths with less extremal widths compared to techniques from existing literature.

A beading strategy is defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading strategies we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_\text{pref} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( b^{-1}(n) / w_\text{pref}  - n \right) \\
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

@@

\section{Validation}
In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the dataset and selected 300 random slices from the total set of slices for thorough analysis.
We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the constant bead count strategy with a bead count of $C=4$, the centered beading strategy, the evenly distributed, and the inward distributed beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

@@

We calculated the total overfill and underfill areas of the different toolpath strategies applied on the dataset. 
The overfill and underfill area as a percentage of the total area of the slices from the dataset are illustrated in \cref{over_underfill}.  
The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the dataset.

@@

\paragraph{Uniformity}
Depending on the printer hardware configuration, some bead widths might be difficult or impossible to manufacture.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
Also, large bead widths can cause the extruded material to bulge upwards instead of filling the required width.
\todo{Include picture of flutter?}
Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.

@@

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive segments generated by each strategy.
The relative frequency of these angles is shown in \cref{smoothness}.
All strategies show a higher number of corners below 45 degrees, with a peak towards 0 degrees.
While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the other strategies.

@@

The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the depositioning control system some of the prints show defects.
Such defects are less prevalant for the inward distributed beading strategy than the other strategies.

@@

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
\caption{Naive}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the naive strategy, center deivation strategy and the inward distributed strategy.
The naive method produces distinct underfill areas.
The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed strategy produces the least defects.
}
\label{prints}
\end{figure}

@@

%We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.
